---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# comunista

<!-- badges: start -->
<!-- badges: end -->

The goal of comunista is to clean up accents from municipality names of Chile and gets them in proper format to make joining datasets by municipality easier.


## Installation

You can install the development version of comunista from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lhersko/comunista")
```
If you use pacman, you can install it using: 

```
# install.packages("pacman")
# library(pacman)
p_load_gh("lhersko/comunista")
```

## Example

To use the clean_comunas() function first specify your data frame name and then the variable that contains municipality names in quotations. For example:

```{r example}
library(comunista)
df <- data.frame(comunas=c("ñuñoa", "Peñalolén", "PEñaflor", "Las condes"))
clean_comunas(df, "comunas")
```


To use the code_comunas() function first specify your data frame name and then the variable that contains municipality names in quotations. For example:

```{r example 2}
library(comunista)
df <- data.frame(comunas=c("ñuñoa", "Peñalolén", "PEñaflor", "Las condes"))
df_clean <- clean_comunas(df, "comunas")
code_comunas(df_clean, "comunas")
```
 
It is strongly suggested that you run clean_comunas() on your data before running code_comunas().
